### 2019-06-14 README.Rmd
updated to do list

@@

**Current Week**

- finish writing and editing introduction
- draft background section
- fix outline of the rest of the paper now that I have a clear vision

@@

#### app

@@

- **app.R**: code for the Shiny app

#### code

@@

- **helper_functions.R**: R script with functions that I use in the journals and will probably end up using in the papers as well

#### data

@@

- **hamby173and252_train.csv**: training data that I cleaned (it should match the data used to fit `rtrees`)
- **hamby224_bin_boundaries.rds**: contains the boundaries for the bins as created by the `lime` function for each of the LIME input settings from the single implementation 
- **hamby224_bins.rds**: contains nice forms of the bin intervals (i.e. [lower, upper)) created using the bin boundaries for each of the LIME input settings from the single implementation 
- **hamby224_explain**: the output from the `explain` function in lime from the single implementation with all of the different input options
- **hamby224_lime**: the output from the `lime` function in lime from the single implementation with all of the different input options
- **hamby224_lime_comparisons**: a dataset with summaries of the LIME explanations from the single implementation with all of the different input options
- **hamby224_lime_inputs**: LIME input settings used for the single implementation of LIME
- **hamby224_sensitivity_inputs**: LIME input settings used for the sensativity analysis of LIME
- **hamby224_sensitivity_joined.csv**: the test data and the LIME explanations from the sensativty analysis joined in a dataframe
- **hamby224_sensitivity_outputs.rds**: outputs from the `explain` function applied for each of the different input settings from the sensativity analysis combined in one dataframe
- **hamby223_test.csv**: testing data that I cleaned (created from sets 1 and 11 of the Hamby 224 study)
- **hamby224_test_explain.rds**: dataframe with the testing data and the output LIME explanation data from the single implementation with all of the different input options
- raw: original data given to me by Heike
    - **features-hamby173and252.csv**
    - **h224-set1-features.rds**
    - **h224-set11-features.rds**

#### journals

@@

- **00-objectives_and_ideas**: background of the research project, goals of the project, concerns with LIME, and ideas to try
- **01-training_and_testing_data**: information on the Hamby data, understanding the raw data, and cleaning of the training and testing data
- **02-plotting_training_and_testing_data**: exploratory plots of the training and testing data
- **03-computation_issues**: documentation of some of the computation issues I ran into during the project
- **04-lime_algorithm_and_proposed_methods**: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
- **05-applying_lime_to_rtrees**: application of lime and sensativity analysis for many different input options
- **06-assessing_lime_explanations**: assessment of the lime explanations
- **07-logistic_regression**: logistic regressions fit to the bullet data and application of lime to the logistic regression
- **08-iris_comparison**: applying LIME to a random forest fit to the iris data
- **09-understanding_lime**: attempts to visualize the results from LIME to understand how LIME works
- **10-other_explainers**: trying out other model explainers
- **notes from Heike.pdf**: scans of notes written by Heike for this project

#### papers

@@

- **bullet_application**: explains how LIME can be used to understand the random forest model fit to bullet matching data
- **lime_diagnostics**: explains the need to assess LIME and presents some visual diagnostic tools

>>>>

- can I remove some of the sources from the references file that I am not going to use?
- I finished writing and editing the introduction - what do you think?

@@

**Current**

- draft background section
- fix outline of the rest of the paper now that I have a clear vision
- read through papers giving an overview of the current explanation methods

@@

**app**

@@

- `app.R`: code for the Shiny app

**code**

@@

- `helper_functions.R`: R script with functions that I use in the journals and will probably end up using in the papers as well

**data**

@@

- `hamby173and252_train.csv`: training data that I cleaned (it should match the data used to fit `rtrees`)
- `hamby224_bin_boundaries.rds`: contains the boundaries for the bins as created by the `lime` function for each of the LIME input settings from the single implementation 
- `hamby224_bins.rds`: contains nice forms of the bin intervals (i.e. [lower, upper)) created using the bin boundaries for each of the LIME input settings from the single implementation 
- `hamby224_explain`: the output from the `explain` function in lime from the single implementation with all of the different input options
- `hamby224_lime`: the output from the `lime` function in lime from the single implementation with all of the different input options
- `hamby224_lime_comparisons`: a dataset with summaries of the LIME explanations from the single implementation with all of the different input options
- `hamby224_lime_inputs`: LIME input settings used for the single implementation of LIME
- `hamby224_sensitivity_inputs`: LIME input settings used for the sensativity analysis of LIME
- `hamby224_sensitivity_joined.csv`: the test data and the LIME explanations from the sensativty analysis joined in a dataframe
- `hamby224_sensitivity_outputs.rds`: outputs from the `explain` function applied for each of the different input settings from the sensativity analysis combined in one dataframe
- `hamby223_test.csv`: testing data that I cleaned (created from sets 1 and 11 of the Hamby 224 study)
- `hamby224_test_explain.rds`: dataframe with the testing data and the output LIME explanation data from the single implementation with all of the different input options
- raw: original data given to me by Heike
    - `features-hamby173and252.csv`
    - `h224-set1-features.rds`
    - `h224-set11-features.rds`

**journals**

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-training_and_testing_data`: information on the Hamby data, understanding the raw data, and cleaning of the training and testing data
- `02-plotting_training_and_testing_data`: exploratory plots of the training and testing data
- `03-computation_issues`: documentation of some of the computation issues I ran into during the project
- `04-lime_algorithm_and_proposed_methods`: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
- `05-applying_lime_to_rtrees`: application of lime and sensativity analysis for many different input options
- `06-assessing_lime_explanations`: assessment of the lime explanations
- `07-logistic_regression`: logistic regressions fit to the bullet data and application of lime to the logistic regression
- `08-iris_comparison`: applying LIME to a random forest fit to the iris data
- `09-understanding_lime`: attempts to visualize the results from LIME to understand how LIME works
- `10-other_explainers`: trying out other model explainers
- `notes from Heike.pdf`: scans of notes written by Heike for this project

**papers**

@@

- `bullet_application`: explains how LIME can be used to understand the random forest model fit to bullet matching data
- `lime_diagnostics`: explains the need to assess LIME and presents some visual diagnostic tools
